---
title: "Untitled"
author: "Zeyu Xiao"
date: "2021/10/8"
output: html_document
---

```{r setup, include=FALSE}
setwd("C:\\Users\\Administrator\\Desktop\\Bike\\")
library(tidyverse)
library(lubridate)
BikeSeoul <- read_csv("BikeSeoul.csv")
BikeWashingtonDC <- read_csv("BikeWashingtonDC.csv")

```

## Data wrangling
```{r cars}
BikeSeoul <- BikeSeoul %>%
  ## remove columns
  select("Date","Rented Bike Count","Hour","Temperature(C)","Humidity(%)", 
         "Wind speed (m/s)","Seasons","Holiday","Functioning Day") %>%
  filter(`Functioning Day`=="Yes")%>% #filter out observations,
  ## remove the functioning day
  select(- "Functioning Day") %>%
  ## change the name of the columns
  rename(Count = "Rented Bike Count",
         Temperature = "Temperature(C)",
         Humidity = "Humidity(%)",
         WindSpeed = "Wind speed (m/s)",
         Season = Seasons) %>%
  ## convert Date to date object
  mutate(Date =  as.Date(Date, "%d/%m/%Y"),
         ## Create a new variable called FullDate
         FullDate = make_datetime(year = year(Date),
                                  month = month(Date),
                                  day = day(Date), 
                                  hour = Hour), 
         ## Change the factor levels of Holiday
         Holiday = factor(Holiday,levels = c("Holiday","No Holiday"), labels = c("Yes","No")),
         ## Change the order of the Season factor levels
         Season = factor(Season, levels = c("Spring", "Summer", "Autumn", "Winter"))
  )

BikeWashingtonDC <- BikeWashingtonDC %>%
  ## remove columns
  select("dteday", "cnt", "hr", "temp", "hum", "windspeed", "season", "holiday")%>%
  ## change the name of the columns
  rename(Date = "dteday", Season = "season",Hour = "hr",Holiday = "holiday", 
         Temperature = "temp",Humidity = "hum", WindSpeed = "windspeed", Count = "cnt")%>% 
  ## Convert Humidity
  mutate(Humidity = Humidity*100,
         ## Convert Temperature
         Temperature = Temperature*(39+8)-8,
         ## Convert WindSpeed
         WindSpeed = WindSpeed*67/3.6,
         ## Change the order of the Season factor levels
         Season = factor(Season, levels = c("1", "2", "3", "4"), labels = c("Spring", "Summer", "Autumn", "Winter")),
         ## Change the factor levels of Holiday
         Holiday = factor(Holiday,levels = c("1","0"), labels = c("Yes","No")),
         ## convert Date to date object
         Date =  as.Date(Date),
         ## Create a new variable called FullDate
         FullDate = make_datetime(year = year(Date),
                                  month = month(Date),
                                  day = day(Date), 
                                  hour = Hour)
  )

```

## How does air temperature varies over the course of a year?
```{r pressure, echo=FALSE}
ggplot(BikeSeoul, aes(Season, Temperature, fill=Season)) +
  geom_boxplot() +
  theme_bw() +
  labs(y = "Temperature in the Seoul")

ggplot(BikeWashingtonDC, aes(Season, Temperature, fill=Season))+
  geom_boxplot() +
  theme_bw() +
  labs(y = "Temperature in the Washington")
```
Seoul has the highest temperature in summer and the lowest temperature in winter. Spring and autumn temperatures are relatively close to each other. In Washington, D.C., temperatures are highest in the autumn, lowest in the spring, and slightly warmer in the summer than in the winter.

Temperatures in these two cities have completely different trends with the seasons, with spring and summer temperatures in Seoul being significantly higher than those in Washington, D.C., and autumn and winter temperatures in Seoul being significantly lower than those in Washington, D.C.


## How does air temperature varies over the course of a year?
```{r}
BikeSeoul %>%
  group_by(Season) %>%
  summarise(mean_count = mean(Count)) %>%
  ggplot(aes(Season, mean_count, fill=Season)) +
  geom_col() +
  theme_bw() +
  labs(y = "Average number of rented bikes in the Seoul")

BikeWashingtonDC %>%
  group_by(Season) %>%
  summarise(mean_count = mean(Count)) %>%
  ggplot(aes(Season, mean_count, fill = Season)) +
  geom_col() +
  theme_bw() +
  labs(y = "Average number of rented bikes in the Washington")
```
In Seoul, the average number of rental bikes was highest in the summer, higher in the autumn than in the spring, and significantly lower in the winter than in the other three seasons. In Washington, D.C., the average number of bicycles rented was highest in the autumn, slightly lower in the summer and winter than in the autumn, and significantly lower in the spring than in the other three seasons.

In both cities, the trend in average number of rental bicycles over the seasons is almost identical to the trend in temperature over the seasons.


## Do holidays increase or decrease the demand for rented bikes?
```{r}
BikeSeoul %>%
  group_by(Holiday) %>%
  summarise(mean_count = mean(Count)) %>%
  ggplot(aes(Holiday, mean_count, fill = Holiday)) +
  geom_col() +
  theme_bw() +
  labs(y = "Average number of rented bikes in the Seoul")

BikeWashingtonDC %>%
  group_by(Holiday) %>%
  summarise(mean_count = mean(Count)) %>%
  ggplot(aes(Holiday, mean_count, fill = Holiday)) +
  geom_col() +
  theme_bw() +
  labs(y = "Average number of rented bikes in the Washington")
```

Both cities have lower numbers of rental cars on holidays than on non-holidays, suggesting that there is less demand for rental cars on holidays.



## How does the time of day affect the demand for rented bikes?
```{r}
BikeSeoul %>%
  group_by(Hour) %>%
  summarise(mean_count = mean(Count)) %>%
  ggplot(aes(Hour, mean_count)) +
  geom_point(col = "red") +
  geom_line() +
  theme_bw() +
  labs(y = "Average number of rented bikes in the Seoul")

BikeWashingtonDC%>%
  group_by(Hour)%>%
  summarise(mean_count = mean(Count))%>%
  ggplot(aes(Hour,mean_count))+
  geom_point(col="red")+
  geom_line()+
  theme_bw()+
  labs(y = "Average number of rented bikes in the Washington")
```
The average number of bicycle rentals in both cities follows much the same trend as the time of day, showing a downward trend between the hours of 18:00 and 4:00 am and 8:00 and 10:00 am. Other times of the day basically show an upward trend. The average number of bicycle rentals in both cities reaches its lowest value at 4 a.m. and its highest value at 18:00 a.m. and 19:00 a.m. in Seoul and Washington, D.C., respectively.

The time of day affects the demand for rental bikes as the demand for rental bikes is relatively high during commuting hours and relatively low during break times.


## Is there an association between bike demand and the three meteorological variables (air temperature,wind speed and humidity)?---（Seoul）
```{r}
ggplot(BikeSeoul,aes(Temperature,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Seoul",
       x = "The temperature (degree Celsius) in the Seoul " )

ggplot(BikeSeoul,aes(WindSpeed,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Seoul",
       x ="The windspeed (m/s) in the Seoul " )

ggplot(BikeSeoul,aes(Humidity,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Seoul",
       x = "The humidity (a%) in the Seoul" )
```

In Seoul, temperature was positively correlated with the number of rented bicycles when the temperature was below 30 degrees. However, when the temperature exceeded 30 degrees, the degree was negatively correlated with the number of rented bicycles. When the wind speed was less than 3 m/s, the wind speed was slightly positively correlated with the number of rented bicycles. When the wind speed exceeded 3 m/s, the wind speed was slightly negatively correlated with the number of rented bicycles. When the humidity was below 50%, the humidity was slightly positively correlated with the number of rented bicycles. When the humidity is higher than 50%, humidity is slightly negatively correlated with the number of rental bikes. The correlation between wind speed and humidity and the number of bicycles rented was weak.


## Is there an association between bike demand and the three meteorological variables (air temperature,wind speed and humidity)?---（Washington）
```{r}
ggplot(BikeWashingtonDC,aes(Temperature,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Washington",
       x = "The temperature (degree Celsius) in Washington" )

ggplot(BikeWashingtonDC,aes(WindSpeed,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Washington",
       x ="The windspeed (m/s) in the Washington " )

ggplot(BikeWashingtonDC,aes(Humidity,Count))+
  geom_point(col="skyblue",size = 0.7)+
  stat_smooth(method = 'loess', formula = 'y ~ x')+
  theme_bw()+
  labs(y = "The number of rented bikes in the Washington",
       x ="The humidity (a%) in the Washington" )
```

In Washington, DC, temperature was positively correlated with the number of bicycles rented, and wind speed was slightly positively correlated with the number of bicycles rented when wind speed was less than 5 m/s. When wind speed exceeded 5 m/s, wind speed was slightly negatively correlated with the number of rented bicycles. There was no significant correlation between wind speed and the number of rented bicycles. When humidity was below 25%, there was a slight positive correlation between humidity and the number of bicycles rented. When humidity was above 25%, humidity showed a negative correlation with the number of bicycles rented.


## Statistical modelling---（Seoul）
```{r}
model_Seoul <- lm(log(Count)~Season + Temperature + Humidity + WindSpeed, data = BikeSeoul)
summary(model_Seoul)

```
In the Seoul model,The residuals first quartile (1Q) and third quartile (Q3) have approximately the same magnitude, implying a more symmetrical distribution.
Among the seasonal variables, the p-value for summer is 0.91247, which is greater than 0.05, indicating that the logarithmic number of bicycle rentals in summer is not significant.
The p-value for wind speed is 0.00668, which is less than 0.05, indicating that wind speed is significant for the log number of bicycles rented.
The adjusted R-squared is 0.4937, indicating that 49.37% of the variance in the number of rented bicycles after logarithmization can be explained by the linear model.


```{r}
model_Washington <- lm(log(Count)~Season + Temperature + Humidity + WindSpeed, data = BikeWashingtonDC)
summary(model_Washington)
```
In the Washington, .DC. model, The residuals first quartile (1Q) and third quartile (Q3) have approximately the same magnitude, implying a more symmetrical distribution.
Among the seasonal variables, the p-value for summer is 0.00218, which is less than 0.05,indicating that the logarithmic number of bicycle rentals in summer is  significant.
The adjusted R-squared is 0.2777, indicating that 27.77% of the variance in the number of rented bicycles after logarithmization can be explained by the linear model.


```{r}
confint(model_Seoul, level = 0.97)
round(exp(predict(model_Seoul,newdata = data.frame(Season="Winter",
                                                   Temperature =0,
                                                   Humidity=20,
                                                   WindSpeed=0.5),interval = "prediction",level = 0.9)),0)
```
When the confidence level increases, the length of the confidence interval increases, and the reliability of the confidence interval decreases.The reliability of the 97% confidence interval is lower compared to the 95% confidence interval.

In Seoul ,the 90% prediction interval of the expected number of rented bikes for that hour when the winter temperature is freezing (0◦ C), with a light wind (0.5 m/s) and 20% humidity is (95,1445).


## Statistical modelling---（Washington）
```{r}
confint(model_Washington,level = 0.97)
round(exp(predict(model_Washington,newdata = data.frame(Season="Winter",
                                                        Temperature =0,
                                                        Humidity=20,
                                                        WindSpeed=0.5),interval = "prediction",level = 0.9)),0)
```
When the confidence level increases, the length of the confidence interval increases, and the reliability of the confidence interval decreases.The reliability of the 97% confidence interval is lower compared to the 95% confidence interval.

And In Washington D.C. ,the 90% prediction interval of the expected number of rented bikes for that hour wwhen the winter temperature is freezing (0◦ C), with a light wind (0.5 m/s) and 20% humidity is (14,886).
